### 2023-03-26 paper.tex
Two working \textstack implementations

\documentclass{sigtbd17-style}
% \documentclass[SIGTBD-cameraready]{sigplanconf-SIGTBD16}

{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}\protect\namestack{Erik Demaine;Martin Demaine}}}

%
% the following standard packages may be helpful, but are not required
%
\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

% Usage: \textstack{\textitem{item1}\textitem{item2}...}
\newcommand\textstack[1]{\strut\vbox to 0pt{\def\textstacksep{}#1}\ignorespaces}
\newcommand\textitem[1]{\textstacksep\hbox{\smash{#1}}\def\textstacksep{\vss}\ignorespaces}

\let\textstack=\relax

\usepackage[final]{pdfcomment}

% Usage: \textstack{item1; item2; ...}
% Or: \textstack[sep]{item1 sep item2 sep ...}
% Loop iteration based on https://tex.stackexchange.com/a/159177/245104
\makeatletter
\newcommand\textstack[2][;]{%
  \def\textstack@sep{}% becomes \vss after one step
  % Append separator (#1) and \@eol to end of input:
  \def\textstack@append##1{\expandafter\textstack@step##1#1\@eol}%
  % Split into first component (##1) up to separator (#1), and rest (##2):
  \def\textstack@step##1#1##2\@eol{%
    \textstack@sep % possible \vss to overlap with previous item
    \hbox{\smash{\ignorespaces ##1\unskip}}%
    \def\textstack@sep{\vss}%
    \ifx\@eol##2\@eol\else\textstack@step##2\@eol\fi}%
  % Make full-height overall vertical size of stack
  \strut
  % Tooltip with full author list
  \pdftooltip{%
    % Crush contents to zero vertical height
    \vbox to 0pt{\textstack@append{#2}}%
  }{#2}%
}
\makeatother

\usepackage{transparent}
\newcommand\namestack[1]{\texttransparent{0.666}{\textstack{#1}}}

\begin{document}

\title{Every Author as First Author}

%
% any author declaration will be ignored  when using 'SIGTBD' option (for double blind review)
%

\authorinfo{\namestack{Erik Demaine; Martin Demaine}}
{\makebox{Computer Science and Artificial Intelligence Laboratory} \\
\makebox{Massachusetts Institute of Technology}  \\
\makebox{Cambridge, MA 02139}}
{\namestack{edemaine;mdemaine}@mit.edu}

\maketitle

\begin{abstract}
  We propose a new technology for writing author names on papers
  and in bibliographies, which places \emph{every author as a first author},
  superimposed.
  This approach enables authors to write papers as true equals,
  without any advantage given to e.g.\ whoever's name
  happens to be alphabetically first.
\end{abstract}

\section{Introduction}

intro here.

\bibliographystyle{abbrvnat}

% We recommend that you use BibTeX.  The inlined bibitems below are
% used to keep this template to a single file.
\begin{thebibliography}{}
\softraggedright

\bibitem[Backus et~al.(1960)]{Backus:60}
J.~W. Backus, F.~L. Bauer, J.~Green, C.~Katz, J.~McCarthy, A.~J. Perlis,
  H.~Rutishauser, K.~Samelson, B.~Vauquois, J.~H. Wegstein, A.~van Wijngaarden,
  and M.~Woodger.
\newblock Report on the algorithmic language ALGOL 60.
\newblock \emph{Commun. ACM}, 3\penalty0 (5):\penalty0 299--314, May 1960.
\newblock ISSN 0001-0782.
\newblock \doi{10.1145/367236.367262}.

\bibitem[Collins(1960)]{Collins:60}
G.~E. Collins.
\newblock A method for overlapping and erasure of lists.
\newblock \emph{Commun. ACM}, 3\penalty0 (12):\penalty0 655--657, December
  1960.
\newblock \doi{10.1145/367487.367501}

\bibitem[Lamport(1994)]{Lamport:94}
L.~Lamport.
\newblock \emph{{\LaTeX: A Document Preparation System}}.
\newblock Addison-Wesley, Reading, Massachusetts, 2nd edition, 1994.

\bibitem[McCarthy(1960)]{McCarthy:60}
J.~McCarthy.
\newblock Recursive functions of symbolic expressions and their computation by
  machine, part {I}.
\newblock \emph{Commun. ACM}, 3\penalty0 (4):\penalty0 184--195, April 1960.
\newblock \doi{10.1145/367177.367199}

\end{thebibliography}

\end{document}

### 2023-03-26 paper.tex
Simpler and better version with proper height/depth
Copy/paste override via accsupp
Intro and start of Solution

@@
 
-{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}\protect\namestack{Erik Demaine;Martin Demaine}}}
+{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}\protect\namestack{Erik D. Demaine; Martin L. Demaine}}}
 
@@
 \usepackage[final]{pdfcomment}
+\usepackage{accsupp}
 
@@
 % Or: \textstack[sep]{item1 sep item2 sep ...}
+% Expands to \vbox{\hbox{item1}\vskip-\baselineskip\hbox{item2}...},
+% plus a PDF tooltip and copy/paste override with original text.
 % Loop iteration based on https://tex.stackexchange.com/a/159177/245104
@@
 \newcommand\textstack[2][;]{%
-  \def\textstack@sep{}% becomes \vss after one step
   % Append separator (#1) and \@eol to end of input:
@@
   \def\textstack@step##1#1##2\@eol{%
-    \textstack@sep % possible \vss to overlap with previous item
-    \hbox{\smash{\ignorespaces ##1\unskip}}%
-    \def\textstack@sep{\vss}%
-    \ifx\@eol##2\@eol\else\textstack@step##2\@eol\fi}%
-  % Make full-height overall vertical size of stack
-  \strut
+    \hbox{\ignorespaces ##1\unskip}%
+    \ifx\@eol##2\@eol\else
+      % More steps: unwind vertical space and continue
+      \vskip-\baselineskip
+      \textstack@step##2\@eol
+    \fi}%
   % Tooltip with full author list
   \pdftooltip{%
-    % Crush contents to zero vertical height
-    \vbox to 0pt{\textstack@append{#2}}%
+    \BeginAccSupp{method=pdfstringdef,unicode,ActualText={#2}}%
+      % Wrap stack in \vbox
+      \vbox{\textstack@append{#2}}%
+    \EndAccSupp{}%
   }{#2}%
@@
 
-\authorinfo{\namestack{Erik Demaine; Martin Demaine}}
+\authorinfo{\namestack{Erik D. Demaine; Martin L. Demaine}}
 {\makebox{Computer Science and Artificial Intelligence Laboratory} \\
@@
 \begin{abstract}
-  We propose a new technology for writing author names on papers
-  and in bibliographies, which places \emph{every author as a first author},
-  superimposed.
+  We propose a new standard for writing author names on papers
+  and in bibliographies, which places
+  \emph{every author as a first author --- superimposed}.
   This approach enables authors to write papers as true equals,
-  without any advantage given to e.g.\ whoever's name
-  happens to be alphabetically first.
+  without any advantage given to whoever's name
+  happens to come first alphabetically (for example).
+  We develop the technology for implementing this standard
+  in \LaTeX, \textsc{Bib}\TeX, and HTML;
+  show several examples; and discuss further advantages.
 \end{abstract}
@@
 
-intro here.
+\paragraph{The problem.}
 
+Authorship order makes for fraught debates in academia.
+Perhaps the most common standard is to list authors in reverse order by
+significance of contributions to the work.
+But this quantity is usually difficult to measure,
+and can lead to uncomfortable conversations, arguments, or even feuds.
+For example, are an advisor's leadership and high-level ideas
+more or less important than a student's technical solutions?
+Is one author's technical work more or less important than
+another author's writing of the paper?
+Even if the answer to these questions are clear to you
+(and equal among all authors), authors' contributions are rarely so clearcut.
+And what if the contributions are roughly equal?
+
+In some disciplines, the order has additional codified meanings.
+For example, many natural sciences use the last author position to indicate the
+research supervisor (principle investigator) whose lab housed the work.
+But what if multiple people serve that role, as research becomes
+increasingly collaborative research?
+
+\paragraph{Existing solutions.}
+
+Some disciplines --- such as economics, mathematics, and
+theoretical computer science --- shun the idea of determining authorship order
+and instead use an algorithmically determined order:
+alphabetically increasing by last name.
+In particular, the alphabetical standard is a central tenet of
+\emph{supercollaborative} research \cite{supercollaboration},
+where researchers brainstorm to solve problems as equals,
+and everyone decides for themselves whether they contributed
+enough to be an author.
+The motivation is that it is difficult to compare contributions when
+brainstorming, as failed ideas are often as important as successful ideas,
+and ideas are often as important as technical work.
+Agreeing to alphabetical authorship ahead of time guarantees that everyone
+will be recognized for their contributions, without ever having to argue
+about who contributed what.
+
+The alphabetical approach avoids any uncomfortable conversations and arguments,
+and works well when contributions are roughly equal or difficult to compare.
+But in practice, we have occasionally seen authors who feel slighted
+by being listed late despite having contributed significantly more than others
+(e.g., having led the research and/or paper).
+
+Other disciplines offer footnotes to clarify authorship order. For example,
+multiple authors can be marked ``joint first author'' to indicate
+equal contributions, or multiple authors can be marked as having
+``jointly supervised'' the work.
+In these cases, the authors in the same category
+are normally listed alphabetically.
+When all authors contributed roughly equally,
+many papers include a footnote explaining that authorship order is alphabetical
+(especially in publication venues where this is not the standard).
+\emph{Nature} encourages including author contribution statements which
+specify each author's exact contribution to the work.
+% https://www.nature.com/nature-portfolio/editorial-policies/authorship#author-contribution-statements
+
+\paragraph{Bias.}
+
+A fundamental limitation to \emph{any} approach that lists the authors
+in a fixed order arises when citing papers with several authors.
+In the body of a paper (as opposed to the bibliography), it is most common
+to write ``X et al.~[\#]''\ when referring to a paper [\#]
+whose first author's last name is X.
+In some styles such as APA, this is built into the citation itself,
+e.g., (X et al., 2023).
+As a result, author X gets their name effectively promoted with every citation,
+which is inconsistent with multiple or all authors being equal.
+
+In our own writing, we try to avoid this practice, and instead
+write all authors' last names whenever citing a paper,
+e.g., ``X, Y, and Z~[\#]''.
+But this workaround becomes impractical for references with ten or more authors.
+
+Beyond listing authors when citing papers,
+other biases arise from alphabetical ordering specifically.
+Bibliography styles where papers are sorted alphabetically (such as ACM's)
+cluster together papers with the same first author, further promoting people
+who have alphabetically early last names so are more likely to be first.
+And of course fields whose standard is not alphabetical ordering
+unfairly judge authorship order of papers that do.
+
+These effects are collectively referred to as
+\emph{alphabetical discrimination} \cite{alphabetical-discrimination}.
+Several studies have explored this phenomenon, and find evidence that
+people with alphabetically earlier last names are more likely to succeed
+academically.
+The present authors have sometimes uncomfortably wondered whether they have
+benefitted in this way, with last names starting with ``D''.
+
+%% https://www.csail.mit.edu/people/?roleFacets=Principal%20Investigators,Core%2FDual,Associates,Emeritus
+%counts={};
+%Array.from(
+%    document.querySelectorAll('.cs-people-result__card__name')
+%).map(x => x.innerText.split(/\s+/).at(-1)[0])
+%.forEach(x => counts[x] = '*' + (counts[x] ?? ''))
+%counts
+
+\section{Solution}
+
+Our proposed solution is a new standard for listing authors on a paper:
+instead of any ordered list, write all author names on top of each other.
+For example, instead of ``Erik Demaine and Martin Demaine'' (alphabetical),
+we write \namestack{Erik Demaine; Martin Demaine}.
+In this way, we achieve the true ideal of an unordered list of equal authors,
+where everyone comes first.
+
+In settings where authors did not contribute equally, we can generalize to
+writing each group of equal authors as an overlapping stack of names.
+For example, when we want to distinguish multiple first authors,
+multiple ``middle'' authors, and multiple supervising authors,
+we can write three distinct groups of authors,
+where each group is overlapping.
+
+\bibliography{paper}
 \bibliographystyle{abbrvnat}
 
-% We recommend that you use BibTeX.  The inlined bibitems below are
-% used to keep this template to a single file.
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Backus et~al.(1960)]{Backus:60}
-J.~W. Backus, F.~L. Bauer, J.~Green, C.~Katz, J.~McCarthy, A.~J. Perlis,
-  H.~Rutishauser, K.~Samelson, B.~Vauquois, J.~H. Wegstein, A.~van Wijngaarden,
-  and M.~Woodger.
-\newblock Report on the algorithmic language ALGOL 60.
-\newblock \emph{Commun. ACM}, 3\penalty0 (5):\penalty0 299--314, May 1960.
-\newblock ISSN 0001-0782.
-\newblock \doi{10.1145/367236.367262}.
-
-\bibitem[Collins(1960)]{Collins:60}
-G.~E. Collins.
-\newblock A method for overlapping and erasure of lists.
-\newblock \emph{Commun. ACM}, 3\penalty0 (12):\penalty0 655--657, December
-  1960.
-\newblock \doi{10.1145/367487.367501}
-
-\bibitem[Lamport(1994)]{Lamport:94}
-L.~Lamport.
-\newblock \emph{{\LaTeX: A Document Preparation System}}.
-\newblock Addison-Wesley, Reading, Massachusetts, 2nd edition, 1994.
-
-\bibitem[McCarthy(1960)]{McCarthy:60}
-J.~McCarthy.
-\newblock Recursive functions of symbolic expressions and their computation by
-  machine, part {I}.
-\newblock \emph{Commun. ACM}, 3\penalty0 (4):\penalty0 184--195, April 1960.
-\newblock \doi{10.1145/367177.367199}
-
-\end{thebibliography}
-
 \end{document}

### 2023-03-26 paper.tex
Working bibliography

@@
-\documentclass{sigtbd17-style}
+\documentclass[natbib,authoryear]{sigtbd17-style}
 % \documentclass[SIGTBD-cameraready]{sigplanconf-SIGTBD16}
@@
 
+%% OLD:
 % Usage: \textstack{\textitem{item1}\textitem{item2}...}
@@
 \let\textstack=\relax
+
+%% NEW:
 
@@
   }{#2}%
+}
+% natbib support
+\def\NAT@nmfmt#1{%
+  \xdef\textstack@expand{#1}%
+  \expandafter\namestack\textstack@expand
 }
@@
 In particular, the alphabetical standard is a central tenet of
-\emph{supercollaborative} research \cite{supercollaboration},
+\emph{supercollaborative} research \citep{supercollaboration},
 where researchers brainstorm to solve problems as equals,
@@
 
+To improve legibility, we write each name in semi-transparent ink
+(currently, $2/3$ opacity).  Compare:
+%
+\begin{itemize}
+\item Opacity $1$\phantom{${}/1$}:
+  \texttransparent{1}{\textstack{Erik Demaine; Martin Demaine}}
+\item Opacity $3/4$:
+  \texttransparent{0.75}{\textstack{Erik Demaine; Martin Demaine}}
+\item Opacity $2/3$:
+  \texttransparent{0.666}{\textstack{Erik Demaine; Martin Demaine}}
+\item Opacity $1/2$:
+  \texttransparent{0.5}{\textstack{Erik Demaine; Martin Demaine}}
+\end{itemize}
+%
+In the future, we may consider using a different opacity depending on the
+number of authors.  More extremely, we could use opacity to indicate the
+relative contribution of each author (when they are unequal), or different
+colors to represent different roles (such as supervisor).
+
+\section{Technology}
+
 \bibliography{paper}
-\bibliographystyle{abbrvnat}
+\bibliographystyle{overlap-abbrvnat}
 

### 2023-03-27 paper.tex
Amusing author orders and BST improvements

@@
 Authorship order makes for fraught debates in academia.
-Perhaps the most common standard is to list authors in reverse order by
-significance of contributions to the work.
+Perhaps the most common standard is to list authors in decreasing order
+by significance of contributions to the work.
 But this quantity is usually difficult to measure,
@@
 
+To compensate for alphabetical discrimination,
+several specific papers have explored alternate strategies
+to automatic authorship order than alphabetical,
+and report the strategy in a footnote.
+These strategies include competition via
+25-game croquet series \cite{croquet},
+2-day backgammon contest \cite{backgammon},
+tennis match \cite{tennis},
+basketball free throws \cite{free-throws},
+arm wrestling \cite{arm-wrestling},
+brownie bake-off \cite{brownie-bakeoff},
+a game of chicken \cite{chicken},
+rock paper scissors \cite{rock-paper-scissors},
+coin toss \cite{coin-toss},
+dice roll \cite{dice},
+the outcome of famous cricket games \cite{cricket},
+currency exchange rate fluctuation \cite{currency-fluctuation},
+dog treat consumption order \cite{dog},
+author height \cite{height},
+fertility \cite{fertility},
+proximity to tenure \cite{tenure-proximity},
+reverse alphabetical order \cite{reverse-alphabetical},
+and degree of belief in the paper's thesis \cite{belief}.
+Others have proposed games such as Russian roulette
+(``publish and perish'') \cite{publish-and-perish}.
+See the excellent surveys \cite{survey1,survey2,survey3}
+and their comments.
+
 %% https://www.csail.mit.edu/people/?roleFacets=Principal%20Investigators,Core%2FDual,Associates,Emeritus

### 2023-03-27 paper.tex
Fix for long author list
Remove ACM from copyright
Bib fixes
Opacity subsection

@@
 
-{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}\protect\namestack{Erik D. Demaine; Martin L. Demaine}}}
+{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}%
+  \rlap{\textcolor{white}{\rule{2.5em}{1em}}}%
+  \protect\namestack{Erik D. Demaine; Martin L. Demaine}}}
 
@@
 %
-\usepackage{courier}            % standard fixed width font
+%\usepackage{courier}            % standard fixed width font
 \usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
-\usepackage{url}                  % format URLs
+\usepackage[hyphens,spaces,obeyspaces]{url}
 \usepackage{listings}          % format code
@@
 
+\subsection{Opacity}
+
 To improve legibility, we write each name in semi-transparent ink
-(currently, $2/3$ opacity).  Compare:
+(currently, $2/3$ opacity).
+As a result, where multiple characters overlap, the ink appears darker,
+making the names more legible.%
+%
+\footnote{Warning: Not all PDF viewers correctly display text transparency
+  as created by \texttt{transparent.sty}.  Notably, Adobe Acrobat on Windows
+  does not seem to darken where multiple layers overlap.}
+%
+Compare:
 %
@@
 In the future, we may consider using a different opacity depending on the
-number of authors.  More extremely, we could use opacity to indicate the
+number of authors.  More extreme, we could use opacity to indicate the
 relative contribution of each author (when they are unequal), or different
 colors to represent different roles (such as supervisor).
+But for now we like the uniformity of every name
+appearing the same in all contexts.
 
@@
 \bibliography{paper}
-\bibliographystyle{overlap-abbrvnat}
+\bibliographystyle{stack-abbrvnat}
 

### 2023-03-27 paper.tex
Flesh out Section 2

@@
   \protect\namestack{Erik D. Demaine; Martin L. Demaine}}}
+
+\usepackage[utf8]{inputenc}
 
@@
 \usepackage{transparent}
-\newcommand\namestack[1]{\texttransparent{0.666}{\textstack{#1}}}
+\newcommand\namestack[2][0.666]{\texttransparent{#1}{\textstack{#2}}}
 
@@
 e.g., ``X, Y, and Z~[\#]''.
-But this workaround becomes impractical for references with ten or more authors.
+But this workaround becomes impractical for references with over a dozen
+authors, such as some of our papers
+\cite{ArithmeticGames_ISAAC2020,LessThanEdgeMatching_JIP}
+% >>> lines=open('edemaine.bib').read().split('\n')
+% >>> import re
+% >>> lines=[(len(re.findall(r'\band\b', line))+1, line) for line in lines]
+% >>> sorted(lines)[-10:]
+or some papers in astronomy \cite{reverse-alphabetical} and
+biology \cite{human-genome}.
 
@@
 
+Our vision is that each set of names (as we often associate with each paper)
+becomes recognizable as its own image.  Readers can then recognize repetitions
+of the same paper without necessarily reading the individual names.
+For example, compare two of our papers with overlapping but differing sets
+of 15 authors each:
+\citet{ArithmeticGames_ISAAC2020} vs.\ \citet{LessThanEdgeMatching_JIP}.
+Each author stack has a distinct shape.
+If we now repeat one --- \citet{ArithmeticGames_ISAAC2020} ---
+you should be able to recognize which it is.
+
+\subsection{Revealing the Names}
+
+Of course, we want to give authors (equal) credit for their papers,
+not remove all credit.
+We have implemented two ways to reveal the actual names present in a stack.
+
+First, hovering over the stacked names should pop up a tooltip with the
+authors listed in their original order.
+In practice, PDF viewers do not seem to display the tooltips for text that is
+also a link to the bibliography, so readers must click on the link and then
+hover over the name stack in the bibliography; hopefully this extra step
+will be unnecessary in the future.
+
+Second, copying and pasting the author stack (together with any surrounding
+text) into another document should reveal the authors in their original order,
+using PDF's accessibility feature.  This makes it easy to quote portions of
+a paper, including any citations, with or without author stacks.
+
 \subsection{Opacity}
@@
 \begin{itemize}
-\item Opacity $1$\phantom{${}/1$}:
-  \texttransparent{1}{\textstack{Erik Demaine; Martin Demaine}}
-\item Opacity $3/4$:
-  \texttransparent{0.75}{\textstack{Erik Demaine; Martin Demaine}}
-\item Opacity $2/3$:
-  \texttransparent{0.666}{\textstack{Erik Demaine; Martin Demaine}}
-\item Opacity $1/2$:
-  \texttransparent{0.5}{\textstack{Erik Demaine; Martin Demaine}}
+\item \namestack[1]{Erik Demaine; Martin Demaine} ~ (opacity $1$, no transparency)
+\item \namestack[0.75]{Erik Demaine; Martin Demaine} ~ (opacity $3/4$)
+\item \namestack[0.666]{Erik Demaine; Martin Demaine} ~ (opacity $2/3$)
+\item \namestack[0.5]{Erik Demaine; Martin Demaine} ~ (opacity $1/2$)
 \end{itemize}
@@
 
+\subsection{\LaTeX}
+
+\subsection{\textsc{Bib}\TeX}
+
+\subsection{HTML}
+
 \bibliography{paper}

### 2023-03-27 paper.tex
Tooltips in \cite!

@@
 \newcommand\namestack[2][0.666]{\texttransparent{#1}{\textstack{#2}}}
+
+%%% Remove links from names so that tooltips are visible.
+%%% Code from https://tex.stackexchange.com/a/27311/2451040
+
+\usepackage{etoolbox}
+\makeatletter
+
+% Patch case where name and year are separated by aysep
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+
+% Patch case where name and year are separated by opening bracket
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+       {\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+  {}{}
+
+\makeatother
 
@@
 authors listed in their original order.
-In practice, PDF viewers do not seem to display the tooltips for text that is
-also a link to the bibliography, so readers must click on the link and then
-hover over the name stack in the bibliography; hopefully this extra step
-will be unnecessary in the future.
+%In practice, PDF viewers do not seem to display the tooltips for text that is
+%also a link to the bibliography, so readers must click on the link and then
+%hover over the name stack in the bibliography; hopefully this extra step
+%will be unnecessary in the future.
+This feature works on all desktop PDF viewers we have tested,
+but does not work on mobile devices we tested
+(probably because they lack a natural notion of ``hovering'').
+Because tooltips and links are both types of PDF annotations, they would
+conflict with each other if used together, so we had to remove hyperlinks
+from names; the years remain clickable links to the bibliography.
 

### 2023-03-28 paper.tex
Clean up alternatives to alphabetical

@@
 To compensate for alphabetical discrimination,
-several specific papers have explored alternate strategies
-to automatic authorship order than alphabetical,
-and report the strategy in a footnote.
-These strategies include competition via
+several specific papers have explored alternate mechanisms
+for deciding authorship order other than alphabetical,
+as documented in a footnote.
+These mechanisms include competition via
 25-game croquet series \cite{croquet},
@@
 brownie bake-off \cite{brownie-bakeoff},
-a game of chicken \cite{chicken},
-rock paper scissors \cite{rock-paper-scissors},
-coin toss \cite{coin-toss},
+a game of chicken \cite{chicken}, or
+rock paper scissors \cite{rock-paper-scissors};
+by coin toss \cite{coin-toss},
 dice roll \cite{dice},
@@
 currency exchange rate fluctuation \cite{currency-fluctuation},
-dog treat consumption order \cite{dog},
-author height \cite{height},
+dog treat consumption order \cite{dog};
+by authors' height \cite{height},
 fertility \cite{fertility},
@@
 reverse alphabetical order \cite{reverse-alphabetical},
-and degree of belief in the paper's thesis \cite{belief}.
+or degree of belief in the paper's thesis \cite{belief}.
 Others have proposed games such as Russian roulette

### 2023-03-28 paper.tex
Add number of authors in parentheses
Space Savings

@@
 For example, compare two of our papers with overlapping but differing sets
-of 15 authors each:
+of 13--15 authors (which came from a common supercollaborative open problem
+session so share many names):
 \citet{ArithmeticGames_ISAAC2020} vs.\ \citet{LessThanEdgeMatching_JIP}.
@@
 
+\subsection{Space Savings}
+
+An additional benefit of our solution is that long lists of names can be
+written in far less space.  This property is especially helpful for conferences
+and journals with a hard limit on the number of pages including the bibliography
+(including many with a printed publication).  For example, the 274 authors of
+the human genome project \cite{human-genome} would normally take almost half
+a page to list:
+
+\begin{quote}\sloppy
+J.~C. Venter, M.~D. Adams, E.~W. Myers, P.~W. Li, R.~J. Mural, G.~G. Sutton,
+  H.~O. Smith, M.~Yandell, C.~A. Evans, R.~A. Holt, J.~D. Gocayne,
+  P.~Amanatides, R.~M. Ballew, D.~H. Huson, J.~R. Wortman, Q.~Zhang, C.~D.
+  Kodira, X.~H. Zheng, L.~Chen, M.~Skupski, G.~Subramanian, P.~D. Thomas,
+  J.~Zhang, G.~L.~G. Miklos, C.~Nelson, S.~Broder, A.~G. Clark, J.~Nadeau,
+  V.~A. McKusick, N.~Zinder, A.~J. Levine, R.~J. Roberts, M.~Simon, C.~Slayman,
+  M.~Hunkapiller, R.~Bolanos, A.~Delcher, I.~Dew, D.~Fasulo, M.~Flanigan,
+  L.~Florea, A.~Halpern, S.~Hannenhalli, S.~Kravitz, S.~Levy, C.~Mobarry,
+  K.~Reinert, K.~Remington, J.~Abu-Threideh, E.~Beasley, K.~Biddick,
+  V.~Bonazzi, R.~Brandon, M.~Cargill, I.~Chandramouliswaran, R.~Charlab,
+  K.~Chaturvedi, Z.~Deng, V.~D. Francesco, P.~Dunn, K.~Eilbeck, C.~Evangelista,
+  A.~E. Gabrielian, W.~Gan, W.~Ge, F.~Gong, Z.~Gu, P.~Guan, T.~J. Heiman, M.~E.
+  Higgins, R.~R. Ji, Z.~Ke, K.~A. Ketchum, Z.~Lai, Y.~Lei, Z.~Li, J.~Li,
+  Y.~Liang, X.~Lin, F.~Lu, G.~V. Merkulov, N.~Milshina, H.~M. Moore, A.~K.
+  Naik, V.~A. Narayan, B.~Neelam, D.~Nusskern, D.~B. Rusch, S.~Salzberg,
+  W.~Shao, B.~Shue, J.~Sun, Z.~Wang, A.~Wang, X.~Wang, J.~Wang, M.~Wei,
+  R.~Wides, C.~Xiao, C.~Yan, A.~Yao, J.~Ye, M.~Zhan, W.~Zhang, H.~Zhang,
+  Q.~Zhao, L.~Zheng, F.~Zhong, W.~Zhong, S.~Zhu, S.~Zhao, D.~Gilbert,
+  S.~Baumhueter, G.~Spier, C.~Carter, A.~Cravchik, T.~Woodage, F.~Ali, H.~An,
+  A.~Awe, D.~Baldwin, H.~Baden, M.~Barnstead, I.~Barrow, K.~Beeson, D.~Busam,
+  A.~Carver, A.~Center, M.~L. Cheng, L.~Curry, S.~Danaher, L.~Davenport,
+  R.~Desilets, S.~Dietz, K.~Dodson, L.~Doup, S.~Ferriera, N.~Garg,
+  A.~Gluecksmann, B.~Hart, J.~Haynes, C.~Haynes, C.~Heiner, S.~Hladun,
+  D.~Hostin, J.~Houck, T.~Howland, C.~Ibegwam, J.~Johnson, F.~Kalush, L.~Kline,
+  S.~Koduru, A.~Love, F.~Mann, D.~May, S.~McCawley, T.~McIntosh, I.~McMullen,
+  M.~Moy, L.~Moy, B.~Murphy, K.~Nelson, C.~Pfannkoch, E.~Pratts, V.~Puri,
+  H.~Qureshi, M.~Reardon, R.~Rodriguez, Y.~H. Rogers, D.~Romblad, B.~Ruhfel,
+  R.~Scott, C.~Sitter, M.~Smallwood, E.~Stewart, R.~Strong, E.~Suh, R.~Thomas,
+  N.~N. Tint, S.~Tse, C.~Vech, G.~Wang, J.~Wetter, S.~Williams, M.~Williams,
+  S.~Windsor, E.~Winn-Deen, K.~Wolfe, J.~Zaveri, K.~Zaveri, J.~F. Abril,
+  R.~Guigo, M.~J. Campbell, K.~V. Sjolander, B.~Karlak, A.~Kejariwal, H.~Mi,
+  B.~Lazareva, T.~Hatton, A.~Narechania, K.~Diemer, A.~Muruganujan, N.~Guo,
+  S.~Sato, V.~Bafna, S.~Istrail, R.~Lippert, R.~Schwartz, B.~Walenz,
+  S.~Yooseph, D.~Allen, A.~Basu, J.~Baxendale, L.~Blick, M.~Caminha,
+  J.~Carnes-Stine, P.~Caulk, Y.~H. Chiang, M.~Coyne, C.~Dahlke, A.~D. Mays,
+  M.~Dombroski, M.~Donnelly, D.~Ely, S.~Esparham, C.~Fosler, H.~Gire,
+  S.~Glanowski, K.~Glasser, A.~Glodek, M.~Gorokhov, K.~Graham, B.~Gropman,
+  M.~Harris, J.~Heil, S.~Henderson, J.~Hoover, D.~Jennings, C.~Jordan,
+  J.~Jordan, J.~Kasha, L.~Kagan, C.~Kraft, A.~Levitsky, M.~Lewis, X.~Liu,
+  J.~Lopez, D.~Ma, W.~Majoros, J.~McDaniel, S.~Murphy, M.~Newman, T.~Nguyen,
+  N.~Nguyen, M.~Nodell, S.~Pan, J.~Peck, M.~Peterson, W.~Rowe, R.~Sanders,
+  J.~Scott, M.~Simpson, T.~Smith, A.~Sprague, T.~Stockwell, R.~Turner,
+  E.~Venter, M.~Wang, M.~Wen, D.~Wu, M.~Wu, A.~Xia, A.~Zandieh, and X.~Zhu.
+\end{quote}
+
+As a result, many papers that cite this paper do not even list the entire
+author list in the bibliography, instead writing ``J. C. Venter et al.''
+% example: https://www.nature.com/articles/s41586-022-04601-8
+Our approach makes it easy to give the full author list \cite{human-genome},
+giving credit to all authors without allocating that paper a disproportionate
+amount of space in the bibliography.
+
 \section{Technology}
@@
 \bibliographystyle{stack-abbrvnat}
+%\bibliographystyle{abbrvnat}
 

### 2023-03-28 paper.tex
Separate real stuff from joke

@@
 An additional benefit of our solution is that long lists of names can be
-written in far less space.  This property is especially helpful for conferences
-and journals with a hard limit on the number of pages including the bibliography
-(including many with a printed publication).  For example, the 274 authors of
-the human genome project \cite{human-genome} would normally take almost half
-a page to list:
+written in far less space, and roughly the same amount of space for each paper.
+For example, the 274 authors of the human genome project \cite{human-genome}
+would normally take almost half a page to list:
 
@@
 
-As a result, many papers that cite this paper do not even list the entire
-author list in the bibliography, instead writing ``J. C. Venter et al.''
+As a result, many papers that cite this paper do not list the entire
+author list even in the bibliography, instead writing ``J. C. Venter et al.''
 % example: https://www.nature.com/articles/s41586-022-04601-8
 Our approach makes it easy to give the full author list \cite{human-genome},
-giving credit to all authors without allocating that paper a disproportionate
-amount of space in the bibliography.
+giving credit to all authors, but without allocating that paper a
+disproportionate amount of space in the bibliography.
+Thus we help achieve fairness between cited papers, not just between authors
+on each paper.
+
+The space-savings property is also helpful for conferences and journals
+with a hard limit on the number of pages including the bibliography.
+Such limits are common among printed publications.
+For such publications, the space savings also translates to a cost savings
+for the publisher, and a reduction in trees needed to make paper ---
+a helpful step toward resolving the climate crisis.
 

### 2023-03-28 paper.tex
Document \namestack more
LaTeX code

@@
 \usepackage[hyphens,spaces,obeyspaces]{url}
-\usepackage{listings}          % format code
 \usepackage{enumitem}      % adjust spacing in enums
@@
 
+% Theme based on https://tex.stackexchange.com/a/283543/245104
+\usepackage{xcolor}
+\definecolor{commentgreen}{RGB}{2,112,10}
+%\definecolor{eminence}{RGB}{108,48,130}
+%\definecolor{eminence}{RGB}{81,36,97} % 25% darker
+\definecolor{ours}{RGB}{0,71,171} % cobolt blue
+\definecolor{frenchplum}{RGB}{129,20,83}
+\usepackage{listings}
+\lstset{
+  language=[LaTeX]TeX,
+  basicstyle=\ttfamily,
+  numbers=left, numberstyle=\footnotesize,
+  commentstyle=\slshape\color{commentgreen},
+  alsoletter={@},
+  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open},
+  keywordstyle=\color{frenchplum},
+  emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
+  emphstyle=\color{ours}
+  %texcsstyle=*\color{frenchplum}
+}
+
 %% OLD:
+\iffalse
 % Usage: \textstack{\textitem{item1}\textitem{item2}...}
@@
 \newcommand\textitem[1]{\textstacksep\hbox{\smash{#1}}\def\textstacksep{\vss}\ignorespaces}
-
-\let\textstack=\relax
+\fi
 
@@
 
-\usepackage[final]{pdfcomment}
-\usepackage{accsupp}
-
-% Usage: \textstack{item1; item2; ...}
-% Or: \textstack[sep]{item1 sep item2 sep ...}
-% Expands to \vbox{\hbox{item1}\vskip-\baselineskip\hbox{item2}...},
-% plus a PDF tooltip and copy/paste override with original text.
-% Loop iteration based on https://tex.stackexchange.com/a/159177/245104
-\makeatletter
-\newcommand\textstack[2][;]{%
-  % Append separator (#1) and \@eol to end of input:
-  \def\textstack@append##1{\expandafter\textstack@step##1#1\@eol}%
-  % Split into first component (##1) up to separator (#1), and rest (##2):
-  \def\textstack@step##1#1##2\@eol{%
-    \hbox{\ignorespaces ##1\unskip}%
-    \ifx\@eol##2\@eol\else
-      % More steps: unwind vertical space and continue
-      \vskip-\baselineskip
-      \textstack@step##2\@eol
-    \fi}%
-  % Tooltip with full author list
-  \pdftooltip{%
-    \BeginAccSupp{method=pdfstringdef,unicode,ActualText={#2}}%
-      % Wrap stack in \vbox
-      \vbox{\textstack@append{#2}}%
-    \EndAccSupp{}%
-  }{#2}%
-}
-% natbib support
-\def\NAT@nmfmt#1{%
-  \xdef\textstack@expand{#1}%
-  \expandafter\namestack\textstack@expand
-}
-\makeatother
-
-\usepackage{transparent}
-\newcommand\namestack[2][0.666]{\texttransparent{#1}{\textstack{#2}}}
-
-%%% Remove links from names so that tooltips are visible.
-%%% Code from https://tex.stackexchange.com/a/27311/2451040
-
-\usepackage{etoolbox}
-\makeatletter
-
-% Patch case where name and year are separated by aysep
-\patchcmd{\NAT@citex}
-  {\@citea\NAT@hyper@{%
-     \NAT@nmfmt{\NAT@nm}%
-     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
-     \NAT@date}}
-  {\@citea\NAT@nmfmt{\NAT@nm}%
-   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
-
-% Patch case where name and year are separated by opening bracket
-\patchcmd{\NAT@citex}
-  {\@citea\NAT@hyper@{%
-     \NAT@nmfmt{\NAT@nm}%
-     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
-       {\@citeb\@extra@b@citeb}%
-     \NAT@date}}
-  {\@citea\NAT@nmfmt{\NAT@nm}%
-   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
-  {}{}
-
-\makeatother
+\input{namestack}
+\input{stack-natbib}
 
@@
 
+We implemented \LaTeX\ macros for easily superimposing author names
+into an ``overlay stack''.
+A user can build such a stack from a semicolon-separated list of names
+like so:
+
+\begin{center}
+  \lstinline|\namestack{Erik Demaine; Martin Demaine}|
+
+  $\to$ ~
+  \namestack{Erik Demaine; Martin Demaine}
+\end{center}
+
+Listings \ref{lst:namestack} and \ref{lst:natbib}
+
+\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
+\lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}
+
 \subsection{\textsc{Bib}\TeX}

### 2023-03-28 paper.tex
LaTeX code

@@
 This feature works on all desktop PDF viewers we have tested,
-but does not work on mobile devices we tested
+except Chrome%
+\footnote{See \url{https://bugs.chromium.org/p/chromium/issues/detail?id=1122489}}%
+, but does not work on mobile devices we tested
 (probably because they lack a natural notion of ``hovering'').
@@
 
-Listings \ref{lst:namestack} and \ref{lst:natbib}
+\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
 
-\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
+Listing~\ref{lst:namestack} shows the main source code for this macro.
+The main idea is to render each name (into a \TeX\ horizontal box),
+and stack those boxes vertically (in a \TeX\ vertical box)
+with a negative one-line vertical space in between consecutive boxes.
+The example above effectively becomes:
+
+\begin{center}
+\begin{lstlisting}
+\vbox{%
+  \hbox{Erik Demaine}%
+  \vskip-\baselineskip
+  \hbox{Martin Demaine}%
+}%
+\end{lstlisting}
+\end{center}
+
+This main content gets wrapped in three additional components:
+%
+\begin{enumerate}
+\item \lstinline|\texttransparent{0.666}{...}| (from \texttt{transparent.sty})
+  to make the names semi-transparent at opacity $2/3$.
+  The opacity can also be overridden via an optional argument, as in
+  \lstinline|\namestack[0.9]{...}|.
+\item \lstinline|\pdftooltip| (from \texttt{pdfcomment.sty})
+  to add tooltips to the stack, with the original list of names.
+\item \lstinline|\BeginAccSupp{...ActualText=...} ... \EndAccSupp|
+  (from \texttt{accsupp.sty}) to override copy/paste behavior for the stack.
+\end{enumerate}
+
+Listing~\ref{lst:natbib} shows additional code necessary to support
+name/year bibliographies via \texttt{natbib.sty}.  Specifically, we
+automatically wrap the ``name'' portion of a citation in
+\lstinline|\namestack| (so it should be written as a semicolon-separated list).
+We also need to disable hyperlinks on the name portion of each citation,
+to avoid covering the tooltip with another PDF annotation.
+
 \lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}

### 2023-03-29 paper.tex
Tooltip screenshots

@@
 %\usepackage{courier}            % standard fixed width font
+\usepackage{graphicx}
 \usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
@@
 not remove all credit.
-We have implemented two ways to reveal the actual names present in a stack.
+We have implemented two ways to reveal the actual names present in a stack,
+when viewing a PDF file on a computer.
 
 First, hovering over the stacked names should pop up a tooltip with the
-authors listed in their original order.
+authors listed in their original order, as shown in
+Figure~\ref{fig:tooltip}.
 %In practice, PDF viewers do not seem to display the tooltips for text that is
@@
 from names; the years remain clickable links to the bibliography.
+
+\begin{figure}[htbp]
+  \centering
+  \hrule
+
+  \includegraphics[scale=0.5]{figs/tooltip-text.png}
+
+  \hrule
+
+  \includegraphics[scale=0.5]{figs/tooltip-bib.png}
+  \caption{Hovering over a name stack reveals the authors in their original
+    order, as they would normally be written in the citation (above)
+    or bibliography (below).  Screenshots from
+    Visual Studio Code LaTeX Workshop Extension's internal PDF viewer,
+    which is based on PDF.js.}
+    % https://github.com/James-Yu/LaTeX-Workshop/wiki/View
+  \label{fig:tooltip}
+\end{figure}
 

### 2023-03-29 paper.tex
BibTeX code

@@
 %\definecolor{eminence}{RGB}{81,36,97} % 25% darker
-\definecolor{ours}{RGB}{0,71,171} % cobolt blue
+\definecolor{ouridentifier}{RGB}{0,71,171} % cobolt blue
 \definecolor{frenchplum}{RGB}{129,20,83}
+\definecolor{stringorange}{RGB}{139,64,0} % dark orange
+\definecolor{identifieryellow}{RGB}{82,81,0}
 \usepackage{listings}
@@
   emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
-  emphstyle=\color{ours}
+  emphstyle=\color{ouridentifier},
+  stringstyle=\color{stringorange},
+  identifierstyle=\color{identifieryellow},
+  showstringspaces=false
   %texcsstyle=*\color{frenchplum}
 }
+\usepackage{multicol} % enables multicols=2
+
+\def\BibTeX{\textsc{Bib}\TeX}
 
@@
   We develop the technology for implementing this standard
-  in \LaTeX, \textsc{Bib}\TeX, and HTML;
+  in \LaTeX, \BibTeX, and HTML;
   show several examples; and discuss further advantages.
@@
     or bibliography (below).  Screenshots from
-    Visual Studio Code LaTeX Workshop Extension's internal PDF viewer,
-    which is based on PDF.js.}
-    % https://github.com/James-Yu/LaTeX-Workshop/wiki/View
+    VSCode's LaTeX Workshop Extension's internal PDF viewer
+    \cite{latex-workshop-pdf}, which is based on PDF.js.}
   \label{fig:tooltip}
@@
 
-\subsection{\textsc{Bib}\TeX}
+\subsection{\BibTeX}
+
+% Minimal BibTeX mode
+\lstset{
+  alsoletter={$,.},
+  keywords={FUNCTION, if$, while$, for$, swap$, num.names$, format.name$, int.to.str$, write$, newline$, cite$},
+  string=[b]",
+  % Emphasizing function names but not variables
+  emph={namestack, format.names, format.full.names, make.full.names, calc.label, write.label, output.bibitem, before.all, output.state},
+}
+
+We modified the \texttt{abbrvnat.bst} bibliography style requested by this
+proceedings to work with \lstinline|\namestack|;
+refer to Listing~\ref{lst:bst} for the code.
+First, we automatically wrap author/editor names within each bibliography entry
+with \lstinline|\namestack{...}|.
+We also append the number of names in a parenthetical;
+this helps the reader know how many names are in each stack,
+which we find particularly helpful in the context of this paper
+for getting the feel for the newly introduced stacks.
+Second, we output \texttt{natbib.sty}-compatible labels with semicolons
+between all author names (instead of just the first author name followed by
+``et al.''), so that the code in Listing~\ref{lst:natbib} constructs the
+appropriate author stack.
+
+\begin{lstlisting}[float=*,caption={Excerpts from \BibTeX\ style file, including all changed functions from \texttt{abbrvnat.bst}},label=lst:bst,multicols=2]
+%% File: `stack-abbrvnat.bst'
+%% A modification of `abbrv.bst' for use
+%% with natbib package, further modified
+%% for stacking names with \namestack
+
+% Wrap top of stack in \namestack{...}
+FUNCTION {namestack}
+{ "\namestack{" swap$ * "}" *
+}
+
+% Format list of names (author or editor)
+% on top of stack for inclusion in bibitem
+FUNCTION {format.names}
+{ 's :=
+  #1 'nameptr :=
+  s num.names$ 'numnames :=
+  numnames 'namesleft :=
+    { namesleft #0 > }
+    { s nameptr "{f.~}{vv~}{ll}{, jj}"
+      format.name$ 't :=
+      nameptr #1 >
+        { namesleft #1 >
+            { "; " * t * }
+            { t "others" =
+                { " et~al." * }
+                { "; " * t * }
+              if$
+            }
+          if$
+        }
+        't
+      if$
+      nameptr #1 + 'nameptr :=
+      namesleft #1 - 'namesleft :=
+    }
+  while$
+  namestack
+  % Append parenthetical number of names
+  " (" * numnames int.to.str$ * ")" *
+}
+
+% Format list of names (author or editor)
+% on top of stack for inclusion in
+% natbib.sty label (just last names)
+FUNCTION {format.full.names}
+{'s :=
+  #1 'nameptr :=
+  s num.names$ 'numnames :=
+  numnames 'namesleft :=
+    { namesleft #0 > }
+    { s nameptr
+      "{vv }{ll}" format.name$ 't :=
+      nameptr #1 >
+        { "; " * t * }
+        't
+      if$
+      nameptr #1 + 'nameptr :=
+      namesleft #1 - 'namesleft :=
+    }
+  while$
+}
+
+% Omitted because not changed: make.full.names
+% calls format.full.names with author or editor
+
+% Compute label for sorting purposes (not used
+% for actual output because it can overflow)
+FUNCTION {calc.label}
+{
+  make.full.names
+  "(" *
+  year *
+  ")" *
+  'label :=
+}
+
+% Output natbib.sty label, without storing in
+% a variable so won't overflow with many names
+FUNCTION {write.label}
+{
+  make.full.names write$
+  "(" write$
+  year write$
+  ")" write$
+}
+
+FUNCTION {output.bibitem}
+{ newline$
+  "\bibitem[" write$
+  write.label
+  "]{" write$
+  cite$ write$
+  "}" write$
+  newline$
+  ""
+  before.all 'output.state :=
+}
+\end{lstlisting}
 

### 2023-03-29 paper.tex
HTML example

@@
 
-Listing~\ref{lst:namestack} shows the main source code for this macro.
+Listing~\ref{lst:namestack} shows the source code for this macro.
 The main idea is to render each name (into a \TeX\ horizontal box),
@@
 
-\begin{center}
 \begin{lstlisting}
@@
 \end{lstlisting}
-\end{center}
 
@@
 
+\lstset{
+  language=HTML,
+  alsoletter={-},
+  otherkeywords={grid-row, grid-column, opacity, display, inline-grid},
+  emph={stack, name}, % not working because of tag option
+  identifierstyle=
+}
+
+We also give a proof-of-concept that the same style of rendering is
+possible in HTML content.  Figure~\ref{fig:html} shows a rendering
+of the HTML code in Listing~\ref{lst:html}.
+CSS Grid makes implementing an overlapping stack quite easy:
+by placing each name in the same grid cell,
+the cell automatically grows to the maximum size of all names.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.2]{figs/html.png}
+  \caption{Rendering of HTML in Listing~\ref{lst:html}.
+    Screenshot from Google Chrome 111 on Windows 11.}
+  \label{fig:html}
+\end{figure}
+
+\lstinputlisting[caption={HTML source code illustrating a name stack},label=lst:html]{stack.html}
+
+\section{Future Work}
+
 \bibliography{paper}

### 2023-03-29 paper.tex
Future Work and circular arrangements

@@
 
+One limitation of our new standard for listing names is that longer surnames
+gain some bias.
+For example, ``Olds'' (the second half of ``Mitchell-Olds'')
+is clearly visible in \citet{currency-fluctuation}.
+Will this lead to longer and longer academic surnames in the future?
+Arguably, longer names already receive some bias without our system,
+as they take up more relative space in the bibliography.
+Yet in practice so far, most surnames seem to have a similar length.
+The readability of a \emph{suffix} of a surname also does not seem to
+bias the actual name much.
+
+A final issue is that overlapping name stacks are not easy to read.
+It may be possible to write names in a way that has no first name
+but still makes all names clearly readable.
+For example, a circle has no beginning or end, so arranging the names
+in a circular pattern avoids arranging any author ``first''.
+Figure~\ref{fig:circles} shows some initial experiments in this direction.
+It remains unsolved how to fit such circular arrangements
+in with the rest of a document.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/circles}
+  \caption{Circular arrangements of the authors of
+    \citet{LessThanEdgeMatching_JIP}.  Drawn in Inkscape
+    using Circular Align and Distribute, onto a circle of
+    radius 50 (left) or 200 (right); followed by $90^\circ$ rotation
+    (left); and rotating $180^\circ$ to make names upright (bottom).}
+  \label{fig:circles}
+\end{figure}
+
 \bibliography{paper}

### 2023-03-29 paper.tex
sequential
Editing pass

@@
 Perhaps the most common standard is to list authors in decreasing order
-by significance of contributions to the work.
+by significance of contribution.
 But this quantity is usually difficult to measure,
@@
 But what if multiple people serve that role, as research becomes
-increasingly collaborative research?
+increasingly collaborative?
 
@@
 Some disciplines --- such as economics, mathematics, and
-theoretical computer science --- shun the idea of determining authorship order
-and instead use an algorithmically determined order:
-alphabetically increasing by last name.
+theoretical computer science --- discourage the idea of determining authorship
+order by defaulting to an algorithmically determined order:
+alphabetically increasing by surname.
 In particular, the alphabetical standard is a central tenet of
@@
 to write ``X et al.~[\#]''\ when referring to a paper [\#]
-whose first author's last name is X.
-In some styles such as APA, this is built into the citation itself,
-e.g., (X et al., 2023).
+whose first author's surname is X.
+In author--year styles such as APA, this is even built into the citation
+itself, e.g., (X et al., 2023).
 As a result, author X gets their name effectively promoted with every citation,
@@
 In our own writing, we try to avoid this practice, and instead
-write all authors' last names whenever citing a paper,
+write all authors' surnames whenever citing a paper,
 e.g., ``X, Y, and Z~[\#]''.
@@
 cluster together papers with the same first author, further promoting people
-who have alphabetically early last names so are more likely to be first.
+who have alphabetically early surnames so are more likely to be first.
 And of course fields whose standard is not alphabetical ordering
@@
 Several studies have explored this phenomenon, and find evidence that
-people with alphabetically earlier last names are more likely to succeed
+people with alphabetically earlier surnames are more likely to succeed
 academically.
 The present authors have sometimes uncomfortably wondered whether they have
-benefitted in this way, with last names starting with ``D''.
+benefitted in this way, with surnames starting with ``D''.
 
@@
 several specific papers have explored alternate mechanisms
-for deciding authorship order other than alphabetical,
+for deciding authorship order,
+% other than alphabetical,
 as documented in a footnote.
@@
 the outcome of famous cricket games \cite{cricket},
-currency exchange rate fluctuation \cite{currency-fluctuation},
+currency exchange rate fluctuation \cite{currency-fluctuation}, or
 dog treat consumption order \cite{dog};
-by authors' height \cite{height},
+or by authors' height \cite{height},
 fertility \cite{fertility},
@@
 
-Our proposed solution is a new standard for listing authors on a paper:
+Our proposed solution is a new standard for listing the authors of a paper:
 instead of any ordered list, write all author names on top of each other.
@@
 In this way, we achieve the true ideal of an unordered list of equal authors,
-where everyone comes first.
+where every author comes first.
 
-In settings where authors did not contribute equally, we can generalize to
-writing each group of equal authors as an overlapping stack of names.
+In settings where authors did not contribute roughly equally, we can generalize
+to writing each group of equal authors as an overlapping stack of names.
 For example, when we want to distinguish multiple first authors,
@@
 not remove all credit.
-We have implemented two ways to reveal the actual names present in a stack,
-when viewing a PDF file on a computer.
+We have implemented two ways to reveal the actual names present
+in an overlapping stack, when viewing a PDF file on a computer.
 
@@
   \caption{Hovering over a name stack reveals the authors in their original
-    order, as they would normally be written in the citation (above)
-    or bibliography (below).  Screenshots from
+    order, as they would normally be written in the citation (top)
+    or bibliography (bottom).  Screenshots from
     VSCode's LaTeX Workshop Extension's internal PDF viewer
@@
   as created by \texttt{transparent.sty}.  Notably, Adobe Acrobat on Windows
-  does not seem to darken where multiple layers overlap.}
+  does not seem to darken where multiple layers overlap,
+  instead rendering a uniform gray.}
 %
@@
 The main idea is to render each name (into a \TeX\ horizontal box),
-and stack those boxes vertically (in a \TeX\ vertical box)
-with a negative one-line vertical space in between consecutive boxes.
+and stack them vertically (in a \TeX\ vertical box)
+with a negative one-line vertical space in between consecutive names.
 The example above effectively becomes:
@@
   to add tooltips to the stack, with the original list of names.
-\item \lstinline|\BeginAccSupp{...ActualText=...} ... \EndAccSupp|
+\item \lstinline|\BeginAccSupp{...ActualText=...}...\EndAccSupp{}|
   (from \texttt{accsupp.sty}) to override copy/paste behavior for the stack.
@@
 
-We modified the \texttt{abbrvnat.bst} bibliography style requested by this
-proceedings to work with \lstinline|\namestack|;
+We modified the \texttt{abbrvnat.bst} \BibTeX\ bibliography style requested by
+this proceedings to work with \lstinline|\namestack|;
 refer to Listing~\ref{lst:bst} for the code.
@@
 We also give a proof-of-concept that the same style of rendering is
-possible in HTML content.  Figure~\ref{fig:html} shows a rendering
+possible in HTML.  Figure~\ref{fig:html} shows a rendering
 of the HTML code in Listing~\ref{lst:html}.
@@
 The readability of a \emph{suffix} of a surname also does not seem to
-bias the actual name much.
+advantage the actual name much.
 
@@
 It remains unsolved how to fit such circular arrangements
-in with the rest of a document.
+in with the rest of a text document, which feels inherently sequential.
 

### 2023-03-30 paper.tex
Minor edits including better support matrix from feedback

@@
 For example, many natural sciences use the last author position to indicate the
-research supervisor (principle investigator) whose lab housed the work.
+research supervisor (principal investigator) whose lab housed the work.
 But what if multiple people serve that role, as research becomes
@@
 we write \namestack{Erik Demaine; Martin Demaine}.
-In this way, we achieve the true ideal of an unordered list of equal authors,
+In this way, we achieve the true ideal of an unordered set of equal authors,
 where every author comes first.
@@
 %will be unnecessary in the future.
-This feature works on all desktop PDF viewers we have tested,
-except Chrome%
-\footnote{See \url{https://bugs.chromium.org/p/chromium/issues/detail?id=1122489}}%
-, but does not work on mobile devices we tested
+This feature works on many desktop PDF viewers (e.g., Acrobat, Evince, Firefox,
+VSCode), but notably not Chrome%
+\footnote{See \url{https://bugs.chromium.org/p/chromium/issues/detail?id=1122489}},
+Edge, Safari, or MacOS Preview.
+It also does not work on mobile devices we tested
 (probably because they lack a natural notion of ``hovering'').
@@
 text) into another document should reveal the authors in their original order,
-using PDF's accessibility feature.  This makes it easy to quote portions of
-a paper, including any citations, with or without author stacks.
+using PDF's accessibility feature.
+This makes it easy to quote portions of a paper,
+including any citations, with or without author stacks.
+This feature is currently supported by only a few PDF viewers,
+including Acrobat, Chrome, Edge, and Evince.
 
@@
   emph={stack, name}, % not working because of tag option
-  identifierstyle=
+  identifierstyle=,
+  morecomment=[s]{/*}{*/}
 }

### 2023-03-30 paper.tex
PGF-based transparency supporting Acrobat

@@
 As a result, where multiple characters overlap, the ink appears darker,
-making the names more legible.%
-%
-\footnote{Warning: Not all PDF viewers correctly display text transparency
-  as created by \texttt{transparent.sty}.  Notably, Adobe Acrobat on Windows
-  does not seem to darken where multiple layers overlap,
-  instead rendering a uniform gray.}
-%
-Compare:
+making the names more legible.  Compare:
 %

### 2023-03-30 paper.tex
Re-organize listings and improve Future Work

@@
 \usepackage{multicol} % enables multicols=2
+
+% Put figures and text together
+\def\textfraction{0.01}
+\def\topfraction{0.99}
+\def\bottomfraction{0.99}
+\def\floatpagefraction{0.99}
+\def\dblfloatpagefraction{0.99}
 
@@
 
-\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
-
-Listing~\ref{lst:namestack} shows the source code for this macro.
+Listing~\ref{lst:namestack} below shows the source code for this macro.
 The main idea is to render each name (into a \TeX\ horizontal box),
@@
 \begin{enumerate}
-\item \lstinline|\texttransparent{0.666}{...}| (from \texttt{transparent.sty})
-  to make the names semi-transparent at opacity $2/3$.
+\item \lstinline|\textopacity{0.666}{...}| (implemented via \texttt{pgf.sty})
+  to make each name semi-transparent at opacity $2/3$.
   The opacity can also be overridden via an optional argument, as in
@@
 
-\lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}
-
 \subsection{\BibTeX}
-
-% Minimal BibTeX mode
-\lstset{
-  alsoletter={$,.},
-  keywords={FUNCTION, if$, while$, for$, swap$, num.names$, format.name$, int.to.str$, write$, newline$, cite$},
-  string=[b]",
-  % Emphasizing function names but not variables
-  emph={namestack, format.names, format.full.names, make.full.names, calc.label, write.label, output.bibitem, before.all, output.state},
-}
 
@@
 appropriate author stack.
+
+\subsection{HTML}
+
+We also give a proof-of-concept that the same style of rendering is
+possible in HTML.  Figure~\ref{fig:html} shows a rendering
+of the HTML code in Listing~\ref{lst:html}.
+CSS Grid makes implementing an overlapping stack quite easy:
+by placing each name in the same grid cell,
+the cell automatically grows to the maximum size of all names.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.2]{figs/html.png}
+  \caption{Rendering of HTML in Listing~\ref{lst:html}.
+    Screenshot from Google Chrome 111 on Windows 11.}
+  \label{fig:html}
+\end{figure}
+
+\begingroup
+\lstset{
+  language=HTML,
+  alsoletter={-},
+  otherkeywords={grid-row, grid-column, opacity, display, inline-grid},
+  emph={stack, name}, % not working because of tag option
+  identifierstyle=,
+  morecomment=[s]{/*}{*/}
+}
+\lstinputlisting[caption={HTML source code illustrating a name stack},label=lst:html]{stack.html}
+\endgroup
+
+\section{Future Work}
+
+One limitation of our new standard for listing names is that longer surnames
+gain some bias.
+For example, ``Olds'' (the second half of ``Mitchell-Olds'')
+is clearly visible in \citet{currency-fluctuation}.
+Will this lead to longer and longer academic surnames in the future?
+Arguably, longer names already receive some bias without our system,
+as they take up more relative space in the bibliography.
+Yet in practice so far, most surnames seem to have a similar length.
+The readability of a \emph{suffix} of a surname also does not seem to
+advantage the actual name much.
+
+A final issue is that overlapping name stacks are not easy to read.
+It may be possible to write names in a way that has no first name
+but still makes all names clearly readable.
+For example, a circle has no beginning or end, so arranging the names
+in a circular pattern avoids arranging any author ``first''.
+Figure~\ref{fig:circles} shows some initial experiments in this direction.
+It remains unsolved how to fit such circular arrangements
+in with the rest of a text document, which feels inherently sequential.
+Circular arrangements also seem difficult to apply to small numbers of
+authors such as $2$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/circles}
+  \caption{Circular arrangements of the authors of
+    \citet{LessThanEdgeMatching_JIP}.  Drawn in Inkscape
+    using Circular Align and Distribute, onto a circle of
+    radius 50 (left) or 200 (right); followed by $90^\circ$ rotation
+    (left); and rotating $180^\circ$ to make names upright (bottom).}
+  \label{fig:circles}
+\end{figure}
+
+\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
+
+\lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}
+
+% Minimal BibTeX mode
+\lstset{
+  alsoletter={$,.},
+  keywords={FUNCTION, if$, while$, for$, swap$, num.names$, format.name$, int.to.str$, write$, newline$, cite$},
+  string=[b]",
+  % Emphasizing function names but not variables
+  emph={namestack, format.names, format.full.names, make.full.names, calc.label, write.label, output.bibitem, before.all, output.state},
+}
 
@@
 
-\subsection{HTML}
-
-\lstset{
-  language=HTML,
-  alsoletter={-},
-  otherkeywords={grid-row, grid-column, opacity, display, inline-grid},
-  emph={stack, name}, % not working because of tag option
-  identifierstyle=,
-  morecomment=[s]{/*}{*/}
-}
-
-We also give a proof-of-concept that the same style of rendering is
-possible in HTML.  Figure~\ref{fig:html} shows a rendering
-of the HTML code in Listing~\ref{lst:html}.
-CSS Grid makes implementing an overlapping stack quite easy:
-by placing each name in the same grid cell,
-the cell automatically grows to the maximum size of all names.
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[scale=0.2]{figs/html.png}
-  \caption{Rendering of HTML in Listing~\ref{lst:html}.
-    Screenshot from Google Chrome 111 on Windows 11.}
-  \label{fig:html}
-\end{figure}
-
-\lstinputlisting[caption={HTML source code illustrating a name stack},label=lst:html]{stack.html}
-
-\section{Future Work}
-
-One limitation of our new standard for listing names is that longer surnames
-gain some bias.
-For example, ``Olds'' (the second half of ``Mitchell-Olds'')
-is clearly visible in \citet{currency-fluctuation}.
-Will this lead to longer and longer academic surnames in the future?
-Arguably, longer names already receive some bias without our system,
-as they take up more relative space in the bibliography.
-Yet in practice so far, most surnames seem to have a similar length.
-The readability of a \emph{suffix} of a surname also does not seem to
-advantage the actual name much.
-
-A final issue is that overlapping name stacks are not easy to read.
-It may be possible to write names in a way that has no first name
-but still makes all names clearly readable.
-For example, a circle has no beginning or end, so arranging the names
-in a circular pattern avoids arranging any author ``first''.
-Figure~\ref{fig:circles} shows some initial experiments in this direction.
-It remains unsolved how to fit such circular arrangements
-in with the rest of a text document, which feels inherently sequential.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/circles}
-  \caption{Circular arrangements of the authors of
-    \citet{LessThanEdgeMatching_JIP}.  Drawn in Inkscape
-    using Circular Align and Distribute, onto a circle of
-    radius 50 (left) or 200 (right); followed by $90^\circ$ rotation
-    (left); and rotating $180^\circ$ to make names upright (bottom).}
-  \label{fig:circles}
-\end{figure}
-
 \bibliography{paper}

### 2023-03-30 paper.tex
Improve formatting of \textopacity

@@
   alsoletter={@},
-  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open},
+  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open,pgfsetfillopacity,pgfpathmoveto,pgfpointorigin,pgftext},
+  %morekeywords={pgfpicture},
   keywordstyle=\color{frenchplum},
-  emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
+  emph={textopacity,textstack,textstack@step,textstack@append,textstack@expand,namestack},
   emphstyle=\color{ouridentifier},

### 2023-04-03 paper.tex
Cite round-robin documents
hyperref option needed for arXiv

@@
 \usepackage{enumitem}      % adjust spacing in enums
-\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
+\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
 % known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
@@
 Figure~\ref{fig:circles} shows some initial experiments in this direction.
+Related, traditional \emph{round-robin} documents \cite{round-robin}
+are signed by authors in a circle to prevent identification of a ringleader
+(such as mutineer sailors).
 It remains unsolved how to fit such circular arrangements
